Appendix to "Integrated nested Laplace approximations for extended latent Gaussian models with application to the Naomi HIV model

### 2023-01-15 src/docs_paper/appendix.Rmd
Iterate paper and appendix
Add MCMC convergence and suitability section outline to appendix

@@

```{cpp, echo=TRUE, eval=FALSE, output.var="ex", code=readLines("naomi.cpp")}

>>>>

# MCMC convergence and suitability

We assessed MCMC convergence and suitability using a range of graphical and numerical tests.
These included the potential scale reduction factor $\hat R$, bulk and tail effective sample size (ESS), autocorrelation decay plots, univariate traceplots, pairs density plots, and NUTS specific divergent transition and energy assessments.

For the time being, this analysis is available from `athowes.github.io/elgm-inf/mcmc-convergence`.
Once the MCMC results are finalised, the analysis will be moved to this appendix and expanded upon.
The following draft text and references may be useful in that expanded write-up.

* Improved $\hat R$ statistic from @vehtari2021rank. Recommended only to use the sample if the value is less than 1.05.
* ESS and autocorrelation related to efficiency
* Traceplots helpful for diagnosis of problems
* Pairs density plots helpful for understanding relationships between parameters, including possible indentifiability issues
* Energy plot from @betancourt2017conceptual

@@

```{cpp, echo=TRUE, eval=FALSE, output.var="ex", code=readLines("naomi_simple.cpp")}
